To Airbnb?: A Question of Revenue

### 2018-07-24 papers/full_paper.Rmd
Anonymization

---
title: "To Airbnb?: A Question of Revenue"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Greenfield Advisors and University of Melbourne"
date: "July 22nd, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

@@

The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").  In this paper we identify those sitations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one. We also find that hosting policies matter, suggesting that even the right property needs the right owner(s) to make short-term rental the more profitable approach.

@@

All code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.

>>>>

---
title: "To Airbnb?: A Question of Revenue"
#subtitle: "(Andy Krause and Gideon Aschwanden)Rev"
#author: "Greenfield Advisors and University of Melbourne"
date: "Revised: July 22nd, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

@@

The growth of Airbnb and other short-term rental platforms have presented owners of residential properties with a choice of leasing strategy: traditional long-term rental or a short-term approach ("Airbnb-ing").  In this paper we identify those situations -- location, structure type and property characteristics -- that lead to the highest likelihood of favoring a short-term strategy over a long term one. We also find that hosting policies matter, suggesting that even the right property needs the right owner(s) to make short-term rental the more profitable approach.

@@

All code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/anonymousreauthor/to_airbnb](https://www.github.com/anonymousreauthor/to_airbnb)**.

<!--  -->
